\section{Evaluation}

\subsection{Project Objectives}
Comparing the design part to the implementation part, here is a table of what design functions are worked and what are not:\newline
\begin{table}[H]
\centering
\begin{tabular}{|c|p{8cm}|p{2cm}|}
\hline
Operation & Object & Whether it is completed \\
\hline
\multirow{2}{*}{Upload}&{One file (May not in the local sync folder)}&Yes\\
\cline{2-3}
&All files in the local sync folder&Yes\\
\cline{1-3}
\multirow{2}{*}{Download}&{One file}&Yes\\
\cline{2-3}
&All files&Yes\\
\cline{1-3}
\multirow{2}{*}{Delete}&{One file}&Yes\\
\cline{2-3}
&All files&No\\
\cline{1-3}
\multirow{2}{*}{Rename}&{One file}&Yes\\
\cline{2-3}
&Two or more files&No\\
\cline{1-3}
\multirow{2}{*}{Edit}&{One file}&Yes\\
\cline{2-3}
&Two or more files&No\\
\cline{1-3}
\multirow{1}{*}{Synchronize}&{All files in the server and local syn folder}&Yes\\

\bottomrule
\end{tabular}
\caption{Current status of implementation}
\end{table}

\subsection{Team dynamics}
We have worked together in harmony for the most part of the project duration. Team size reduced during the week after the Preliminary report due to conflict. This not only led to redoing of some work but also added work load on the existing members. But the team managed to keep its morale through the whole process.\newline

One of the members had significantly less contributions compared to the rest of the team. This was amplified by lack of communication, attendance and general participation from the member. The gender skew of the team could be a possible reason for this.\newline

Also, sometimes, there was difficulty in communication due to the fact that more than 50\% of the team is Chinese.

The following is the distribution of 100 marks among members. Note that this was assigned with consensus of 4 members as the 5th member was absent on the day the marks were allocated:

\begin{table}[H]
\centering
\begin{tabular}{|c|c|}
\hline
Student Name &  Marks \\
\hline
Georgii Fidarov & 2 \\
\hline
Letao Wang & 24.5 \\
\hline
Lili Chen & 24.5 \\
\hline
Qilin Zhou & 24.5 \\
\hline
Sivaranjani Subramanian & 24.5 \\
\bottomrule
\end{tabular}
\caption{Mark distribution on team consensus}
\end{table}

