
\section{Test}

In the project, our team conducted a black box test on the file synchronization tool. At the beginning, our team tested the transmission of different kinds of file names and file formats. As shown below (Table Black box test result at the beginning). As you can see from the table, we have file names under different language specifications, file names with special symbols, and different types of file formats, such as zip, png, and docx etc. used to do the upload, download, delete and rename function tests. For the uploading, downloading and deleting of files, all the objects we tested can be implemented successfully. However, for the rename function, file names with Chinese names and special symbols cannot be renamed. \newline
At the end of the project, our system implemented automation synchronize function, and these files with Chinese names and special symbols finally achieved in rename function. We analyzed the reason why we couldn't achieve it before because the name of the renamed file needs to be written in the code when we originally developed the product function, and the name with Chinese characters may be inconsistent with the language environment in which the code is written. So, the function cannot be achieved.\newline
Furthermore, we also learned and configuration test environment of Mocha, Chai and Sinon for the desktop application. We try to implement the jsunit test. But for some reasons, it is not complete.\newline

For the desktop client, we found some issues in the test.\\
For the special symbol file we have meet some issues：\\
\begin{itemize}
\item{Pdf file with（“space” “-” "'"） can download but not open. Mostly can open.}
\item{ File name with "'" can be deleted in the local folder but cannot be deleted by using the delete button.}
\item{File with special symbol（*&） can upload but cannot download.}
\item{Irregular naming： \/:*?”<>|, the computer system will show that when we go to rename the file.}
\item{In addition to non-standard named symbols, file names with special symbols cannot be renamed, but a new file is uploaded.}
\end{itemize}

Besides, for the file name with Chinese we also have two issues：\\
\begin{itemize}
\item{Upload from local/download from aws file meet JSON issue because of Chinese word}
\item{Two or more files cannot be deleted, uploaded}
\end{itemize}

The .zip formatted file can be download to local folder from server but it is damaged.



Test case is show below:\\
\begin{table}[H]
\caption{Test Case}
\centering
\begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
\hline
File & \multicolumn{3}{|c|}{Desktop} &\multicolumn{3}{|c|}{Android} \\
\hline
& upload & download & delete & upload & download & delete \\
\hline
Test.txt & T & T & T\\
\hline
123.docx & T & T & T\\
\hline
测试.pdf& F & F & F\\
\hline
!,,!.jpg & T & T & T\\
\hline
测试test.gif& F & F & F\\
\hline
Test!!!.png & T & T & T\\
\hline
123.mp3& T & T & T\\
\hline
2019df.mp4 & T & T & T\\
\hline
!,,!.zip  & T & F & T\\
\hline
Hello.rar& T & T & T\\
\hline
Test!!!.exe& T & T & T\\
\hline
Test.html& T & T & T\\
\hline
2019df.js& T & T & T\\
\hline
'!,,!'.ppt & T & F & F\\
\hline
test123.db & T & T & T\\
\hline
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Test Case}
\centering
\begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
\hline
File & \multicolumn{3}{|c|}{Desktop} &\multicolumn{3}{|c|}{Android} \\
\hline
& Rename to & Rename result & Edit & Rename to & Rename result & Edit  \\
\hline
Test.txt & 123.docx & T & T\\
\hline
123.docx & 测试.pdf& F & T\\
\hline
测试.pdf& !,,!.jpg & F & F\\
\hline
!,,!.jpg & 测试test.gif & F & T\\
\hline
测试test.gif& Test!!!.png & F & F\\
\hline
Test!!!.png & 123.mp3 & T & T\\
\hline
123.mp3& 2019df.mp4 & T & T\\
\hline
2019df.mp4 & !,,!.zip  & T & T\\
\hline
!,,!.zip  & Hello.rar & F & T\\
\hline
Hello.rar& Test!!!.exe & T & T\\
\hline
Test!!!.exe & Test.html & T & T\\
\hline
Test.html& 2019df.js & T & T\\
\hline
2019df.js& '!,,!'.ppt & T & T\\
\hline
'!,,!'.ppt & test123.db & F & T\\
\hline
test123.db & Test.txt & T & T\\
\hline
\bottomrule
\end{tabular}
\end{table}
